2019 Draft Prep

### 2019-03-23 draftPrep.Rmd
Forgot to exclude keepers

Below is a plot of z_score by round so I can identify in which rounds to target specific positions, particularly once we pass to below a z_score of 10. 
```{r echo=FALSE}
positions_ranked_with_keepers %>%
  filter(!keeper,
         ADP <=300) %>%
  group_by(round, position) %>%
  summarize(low = min(z_sum),
            mid = median(z_sum),
            high = max(z_sum),
            n = n()) %>%
  arrange(round) %>%
  ggplot(aes(y=mid, x=round, color=n)) +
  geom_pointrange(aes(ymax = high,ymin = low)) +
  labs(x="Round (ADP)", 
        y="Z_Score") +
  facet_wrap(~ position) -> rv

@@

pitchers_draft %>%
  bind_rows(batters_draft) %>%
  mutate(round = ceiling(ADP/12)) %>%
  arrange(z_sum %>% desc) %>%
  mutate(z_rank = row_number()) %>%
  select(z_rank, Name, z_sum, round, ADP, positions) -> draft_df

draft_df %>% saveRDS("data/draft_dataset.Rds")

draft_df %>%
  head(25) %>%
  kable()
```

>>>>

Below is a plot of z_score by round so I can identify in which rounds to target specific positions, particularly once we pass to below a z_score of 10. 
```{r echo=FALSE}
positions_ranked_with_keepers %>%
positions_ranked_with_keepers %>%
  filter(!keeper,
         ADP <=300) %>%
  group_by(round, position) %>%
  summarize(low = min(z_sum),
            mid = median(z_sum),
            high = max(z_sum),
            n = n()) %>%
  arrange(round) %>%
  ggplot(aes(y=mid, x=round, color=n)) +
  geom_pointrange(aes(ymax = high,ymin = low)) +
  labs(x="Round (ADP)", 
        y="Z_Score") +
  facet_wrap(~ position) -> rv

@@

pitchers_draft %>%
  bind_rows(batters_draft) %>%
  mutate(round = ceiling(ADP/12),
         keeper = (Name %in% keepers)) %>%
  filter(!keeper) %>%
  arrange(z_sum %>% desc) %>%
  mutate(z_rank = row_number()) %>%
  select(z_rank, Name, z_sum, round, ADP, positions) -> draft_df

draft_df %>% saveRDS("data/draft_dataset.Rds")
```
